---
title: "Connecting to Google Geocoding API with package geoloc"
author: "Teno González Dos Santos, Jose Luis López Ruiz, Enrique Josué Álvarez Robles"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette documents the content provided in the package geoloc 1.0.0. This is a high-level adjunct to the low-level details found in *?linearRegression* and *?summary.linreg*. You’ll learn how to work with *geoloc* package by using the previous methods which will allow you to convert adresses into coordinates and vice versa.

```{r, eval = FALSE, include = FALSE}
library(devtools)
devtools::install_github("teno/ARP_Laboratory5", subdir="geoloc")
library(geoloc)
```


## Google Geocoding API

The package *geoloc* works as a connector between the user and the Google Geocoding API. This API converts addresses (like *"1600 Amphitheatre Parkway, Mountain View, CA"*) into geographic coordinates (like latitude 37.423021 and longitude -122.083739), which you can use to place markers on a map, or position the map.

It is also possible to perform **reverse geocoding**, the process of converting geographic coordinates into a human-readable address.

The Google Maps Geocoding API provides a direct way to access these services via an HTTP request, as the following:

```{r, eval = FALSE}
#  https://maps.googleapis.com/maps/api/geocode/json?parameters
```

## Using package *geoloc*


